\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-10-06 introduction.tex
Trying to understand proofs
corrected Isoprimetric Lemma. Went through it with Vardan

Let us provide an informal description of our results and setting. For an
estimator $\theta_n$ with finite quadratic risk (mean squared error) $R_n =
\E_\theta[(\theta_n - \theta)^2]$, we study the limit
\begin{equation}
  \label{eq:ARE_def}
  \limsup_{n\to \infty} n R_n.
\end{equation}
By comparing this quantity to achievable rates of convergence without
communication constraints, we can evaluate the efficiency
losses---asymptotic relative efficiency---of the estimator to appropriately
optimal (unconstrained) estimators. (We shall be more formal in the sequel.)
By lower bounding the quantity~\eqref{eq:ARE_def}, we also provide limits on
estimation of single-bit-per-measurement constrained signals in more general
settings~\cite{baraniuk2017exponential, jacques2013robust, plan2013one,
  li2017channel, choi2016near}.

@@

The remainder of this paper is organized as follows. In Section~\ref{sec:problem} we describe the problem and useful notation. In Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency and MSE. Our main results for the adaptive and distributed cases are given in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively. In Section~\ref{sec:conclusions} we provide concluding remarks.

>>>>

Let us provide an informal description of our results and setting. For an
estimator $\theta_n$ with finite quadratic risk (mean squared error (MSE)) $R_n =
\E_\theta[(\theta_n - \theta)^2]$, we study the limit
\begin{equation}
  \label{eq:ARE_def}
  \limsup_{n\to \infty} n R_n.
\end{equation}
By comparing this quantity to achievable rates of convergence without
communication constraints, we can evaluate the efficiency
losses---asymptotic relative efficiency---of the estimator to appropriately
optimal (unconstrained) estimators. (We shall be more formal in the sequel.)
By lower bounding the quantity~\eqref{eq:ARE_def}, we also provide limits on
estimation of single-bit-per-measurement constrained signals in more general
settings~\cite{baraniuk2017exponential, jacques2013robust, plan2013one,
  li2017channel, choi2016near}.

@@

The remainder of this paper is organized as follows. In
Section~\ref{sec:problem} we describe the problem, notation, and
our basic assumptions. In
Section~\ref{sec:preliminary} we provide two simple bounds on the efficiency
and MSE. Our main results for the adaptive and distributed cases are given
in Sections~\ref{sec:sequential} and \ref{sec:distributed}, respectively. In
Section~\ref{sec:conclusions} we provide concluding remarks.

### 2019-10-06 preliminaries.tex
corrected Isoprimetric Lemma. Went through it with Vardan

When the prior on $\theta$ and the noise corrupting it at each location are
Gaussian, Prabhakaran et al.~\cite{prabhakaran2004rate} characterize the
optimal encoding and its asymptotic risk as $k \to \infty$.  Chen et
al.~\cite{chen2004upper} also provide an expression for the quadratic risk
in the CEO setting under Gaussian priors. Adapting to our setting, this
expression provides the following proposition:
\begin{prop} \label{prop:ceo_lower_bound}
  Assume that $\Theta = \mathbb R$ and $\pi(\theta) =
  \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is
  arbitrary. Then any estimator ${\theta}_n$ of $\theta$ in the distributed
  setting satisfies
  \begin{equation} \label{eq:ceo_bound}
    n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
  \end{equation}
  where the expectation is with respect to $\theta$ and $X^n$.
\end{prop}
\noindent
See Appendix~\ref{app:proof:prop_ceo_lower_bound} for a proof.

>>>>

When the prior on $\theta$ and the noise corrupting it at each location are
Gaussian, Prabhakaran et al.~\cite{prabhakaran2004rate} characterize the
optimal encoding and its asymptotic risk as $k \to \infty$.  Chen et
al.~\cite{chen2004upper} also provide an expression for the quadratic risk
in the CEO setting under Gaussian priors. Adapting to our setting, this
expression provides the following proposition:
\begin{prop} \label{prop:CEO}
  Assume that $\Theta = \mathbb R$ and $\pi(\theta) =
  \Ncal(0,\sigma_\theta^2)$ where $\sigma_\theta^2 \in \mathbb R$ is
  arbitrary. Then any estimator ${\theta}_n$ of $\theta$ in the distributed
  setting satisfies
  \begin{equation} \label{eq:ceo_bound}
    n \ex{\left( \theta - \theta_n \right)^2} \geq \frac{4}{3} \sigma^2 + O(n^{-1}),
  \end{equation}
  where the expectation is with respect to $\theta$ and $X^n$.
\end{prop}
\noindent
See Appendix~\ref{app:proof:CEO} for a proof.

### 2019-10-06 problem-formulation.tex
corrected Isoprimetric Lemma. Went through it with Vardan

To describe our results and make them formal, we require some additional
notation and one main assumption, which restricts the class of distributions
we consider.  We use the typical notation that
$F(x) = \int_{-\infty}^x f(t) dt$ is the cumulative distribution function
of the $X_i$, and we let
\begin{equation*}
  h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
\end{equation*}
be the \emph{hazard} function (or the \emph{failure rate} or \emph{force of
  mortality}), which is monotone increasing as $f$ is
log-concave~\cite{bagnoli2005log}. Given the centrality of the median
to our efficiency bounds, it is unsurprising that the quantity
\begin{equation}
  \label{eq:eta_def}
  \eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))}
  \stackrel{(\star)}{=} \frac{f(x)f(-x)}{F(x)F(-x)}
\end{equation}
appears throughout our development. (Here equality~$(\star)$ is immediate by
the symmetry of $f$.)  For $p \in (0, 1)$ and $x = F^{-1}(p)$,
\begin{equation}
  \label{eqn:variance-quantiles}
  \frac{1}{\eta(x)} =
  \frac{1}{\eta(F^{-1}(p))}
  = \frac{p (1 - p)}{f(F^{-1}(p))^2}
\end{equation}
is of course the familiar asymptotic variance of the $p$th quantile of the
sample $X_1^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).

For $f$ the normal density, it classical results~\cite{Samford1953,
  hammersley1950estimating} show that that $\eta(x)$ is a strictly
decreasing function of $|x|$, as we illustrate in Fig.~\ref{fig:eta}.
%
We consider symmetric log-concave symmetric distributions sharing this
property.  Specifically, we require the following.
\begin{assumption} \label{assump:failure_rate}
  The origin $x = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is
  non-increasing in $|x|$.
\end{assumption}
Under this assumption,
\begin{equation*}
  4 f^2(x) \leq \eta(x) \leq \eta(0),
\end{equation*} 
%
where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median
(Eq.~\eqref{eqn:variance-quantiles} at $p = 1/2$).  Combined with
log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that
$\eta(x)$ vanishes as $|x|\rightarrow \infty$.  Several distributions
satisfy Assumption~\ref{assump:failure_rate}, including the generalized
normal distributions with a shape parameter between $1$ and $2$ (including
the normal and Laplace distributions). Symmetric log-concave distributions
that failing Assumption~\ref{assump:failure_rate} include the uniform
distribution and the generalized normal distribution with shape parameter
greater than $2$. (See Appendix~\ref{sec:uniform-weirdos} for
a brief discussion on the uniform distribution, which illustrates
why some restriction of the class of distributions is necessary to
develop our results; in brief, even one-step adaptive estimators
with a single bit can achieve rates faster than the paramateric
$\sqrt{n}$ convergence for location estimation in the uniform distribution.)

>>>>

To describe our results and make them formal, we require some additional
notation and one main assumption, which restricts the class of distributions
we consider.  We use the typical notation that
$F(x) = \int_{-\infty}^x f(t) dt$ is the cumulative distribution function
of the $X_i$, and we let
\begin{equation*}
  h(x) \triangleq \frac{f(x)}{1-F(x)} = \frac{f(x)}{F(-x)}
\end{equation*}
be the \emph{hazard} function (or the \emph{failure rate} or \emph{force of
  mortality}), which is monotone increasing as $f$ is
log-concave~\cite{bagnoli2005log}. Given the centrality of the median
to our efficiency bounds, it is unsurprising that the quantity
\begin{equation}
  \label{eq:eta_def}
  \eta(x) \triangleq \frac{f^2(x)}{F(x)(1-F(x))}
  \stackrel{(\star)}{=} \frac{f(x)f(-x)}{F(x)F(-x)}
\end{equation}
appears throughout our development. (Here equality~$(\star)$ is immediate by
the symmetry of $f$.)  For $p \in (0, 1)$ and $x = F^{-1}(p)$,
\begin{equation}
  \label{eqn:variance-quantiles}
  \frac{1}{\eta(x)} =
  \frac{1}{\eta(F^{-1}(p))}
  = \frac{p (1 - p)}{f(F^{-1}(p))^2}
\end{equation}
is of course the familiar asymptotic variance of the $p$th quantile of the sample $X_1,\ldots,X^n$ (cf.~\cite{VanDerVaart98}, Ch.~21).

For $f$ the normal density, classical results~\cite{Samford1953,
  hammersley1950estimating} show that that $\eta(x)$ is a strictly
decreasing function of $|x|$, as we illustrate in Fig.~\ref{fig:eta}.
%
We consider log-concave symmetric distributions sharing this
property.  Specifically, we require the following.
\begin{assumption} \label{assump:failure_rate}
  The origin $x = 0$ uniquely maximizes $\eta(x)$, and $\eta(x)$ is
  non-increasing in $|x|$.
\end{assumption}
Under this assumption,
\begin{equation*}
  4 f^2(x) \leq \eta(x) \leq \eta(0),
\end{equation*} 
%
where $\eta(0) = 4 f^2(0)$ is the asymptotic variance of the sample median
(Eq.~\eqref{eqn:variance-quantiles} at $p = 1/2$).  Combined with
log-concavity of $f(x)$, Assumption~\ref{assump:failure_rate} implies that
$\eta(x)$ vanishes as $|x|\rightarrow \infty$.  Several distributions
satisfy Assumption~\ref{assump:failure_rate}, including the generalized
normal distributions with a shape parameter between $1$ and $2$ (including
the normal and Laplace distributions). Symmetric log-concave distributions
that failing Assumption~\ref{assump:failure_rate} include the uniform
distribution and the generalized normal distribution with shape parameter
greater than $2$. (See Appendix~\ref{sec:uniform-weirdos} for
a brief discussion on the uniform distribution, which illustrates
why some restriction of the class of distributions is necessary to
develop our results; in brief, even one-step adaptive estimators
with a single bit can achieve rates faster than the paramateric
$\sqrt{n}$ convergence for location estimation in the uniform distribution.)
